### 2017-02-26 Lab_3/solutions/L3-2-1.tex
Added Lab3 answers and questions file

the tcp connection waits for acks while sending which leads to less collisions than in the udp case which makes it better for low bitrates.

as the bitrates go up, collisions and retransmissions increase and tcp starts to suffer and udp pulls out ahead (affects tcp more than it does udp).

because both tcp and udp have to be sent twice, first from STA1 to the AP and then from the AP to STA2, the achieved throughput is about half of the achieved throughput in the first experiment.

>>>>

\includegraphics[width=0.5\textwidth]{traces/L3-2-1-tput.pdf}
\includegraphics[width=0.5\textwidth]{traces/L3-2-1-usage.pdf}
For low bitrates TCP performs better than UDP. Due to TCP's congestion control there are fewer collisions compared to UDP. For lower bitrates this makes TCP perform better than UDP. For higher bitrates the influence of TCP's additional overhead becomes larger and UDP is more performant than TCP again. \\ \\
For both TCP and UDP, throughput in this case is roughly half of the previous test. Each packet is transmitted twice (to the AP and from the AP), halving the total throughput between source and destination. \\ \\
 The effect of increasing bitrate on the usage is similar to the previous test.

### 2017-02-26 Lab_3/solutions/L3-4-1.tex
Added Lab3 answers and questions file

udp hogere frame length helpt minder, meer botsingen dan verliest er meer dus die capt op een bepaald moment en begint bij 2274 ook weer te dalen

tcp hogere frame length zorgt er voor dat voor constante hoeveelheid overhead er meer data verzonden kan worden dus die blijft in stijgende lijn gaan, ook al is de bereikte tput nog steeds lager dan udp

>>>>

\includegraphics[width=0.5\textwidth]{traces/L3-4-1-tput.pdf} \\
UDP has a fairly small header per datagram. As overhead per datagram is already fairly limited, there is not much room for optimization by putting more data in each datagram. Additionally a larger datagram is more likely to get lost in a wireless network than a smaller one. We observe this when increasing the MTU from 2016 to 2274: the additional packet loss due to the larger frame size outweighs the decrease in per-bit overhead, leading to a lower throughput.
 \\ \\
In the case of TCP there is more per-bit overhead, meaning there is larger room for improvement by putting more data in each segment. Increasing the MTU consistently increases throughput for the tested range: additional packet loss never outweighs the performance increase of reducing the per-bit overhead. This is however never enough to overtake UDP performance.
